First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-05-13 paper/paper.tex
Discuss connection to GHC generics, rearrange appendices

@@

intListSum_helper :: (Int, IntList) -> Int
intListSum_helper p =
  internalize (externalize
    (case p of
       (acc, t) ->
         case t of
           Nil -> acc
           Cons x xs ->
             intListSum_helper
               (x+acc, xs)))

intListSum :: IntList -> Int
intListSum t =
  internalize (externalize
    (intListSum_helper (0, t)))
\end{lstlisting}

\subsection{GHC Generics \ttt{Rep}}

\begin{todo}
  This section is to talk about the details of GHC's generic \ttt{Rep} representation
  and how it is converted to the representation in this paper. Should this section
  exist?
\end{todo}

Any data type with a \ttt{Generic} instance

@@

@@

\begin{lstlisting}
typedef enum var_type_tag {
  EXPR_INT
, EXPR_FLOAT
, EXPR_DOUBLE
, EXPR_CHAR
, EXPR_BOOL
, EXPR_CLOSURE
, EXPR_EITHER_LEFT
, EXPR_EITHER_RIGHT
, EXPR_PAIR
, EXPR_UNIT
, EXPR_STEP
, EXPR_DONE
, EXPR_UNBOXED
} var_type_tag;

@@

\clearpage
\section{Related Work}
\begin{todo}
  Cite and compare/contrast with pattern matching technique described in section
  3.3 of "Unembedding Domain-Specific Languages" (2009; Atkey, Lindley, Yallop)
\end{todo}

@@

macroDef :: CName -> [CName] -> [CCode] -> CCode
macroDef name args theLines =
  unlines
    [ "#define " <> name
              <> "(" <>
                intercalate ", " args
              <> ")\\"
    , "  do {\\"
    , unlines
        . map ("    "++)
        . map (++"\\")
        $ theLines
    , "  } while (0);"
    ]
\end{lstlisting}

% \begin{todo}
%   Fill in
% \end{todo}

>>>>

\subsection{Motivation}

@@

intListSum :: (Int, IntList) -> Int
intListSum p =
  internalize (externalize
    (case p of
       (acc, t) ->
         case t of
           Nil -> acc
           Cons x xs ->
             intListSum
               (x+acc, xs)))
\end{lstlisting}

@@

With GHC Generics, any data type \ttt{T} with a \ttt{Generic} instance has a
corresponding \ttt{Rep T} type, which gives a generic representation of \ttt{T}.
Conversion between values of this type and values of the original type \ttt{T} is
given by the functions \ttt{to} and \ttt{from}. The generic representation \ttt{Rep T}
can be traversed by functions which operate solely on the structure of the data type.
This generic representation contains additional metadata which we do not need.
However, we can automatically generate a \ttt{ERep} instance for any type which
has a \ttt{Generic} instance.

As \ttt{Generic} instances are automatically generated, this provides a simple mechanism
to automaticly generate \ttt{ERep} instances.

@@

\begin{lstlisting}
typedef enum var_type_tag {
  EXPR_INT
, EXPR_PAIR
...
, EXPR_UNIT
} var_type_tag;

@@

\clearpage
\section{Related Work}
\begin{todo}
  Cite and compare/contrast with pattern matching technique described in section
  3.3 of "Unembedding Domain-Specific Languages" (2009; Atkey, Lindley, Yallop)~\cite{Atkey:09:Unembedding}
\end{todo}

@@

macroDef :: CName -> [CName] -> [CCode] -> CCode
macroDef name args theLines =
  unlines
    [ "#define " <> name
              <> "(" <>
                intercalate ", " args
              <> ")\\"
    , "  do {\\"
    , unlines
        . map ("    "++)
        . map (++"\\")
        $ theLines
    , "  } while (0);"
    ]
\end{lstlisting}
% \begin{todo}
%   Fill in
% \end{todo}
